---
title: "individual1"
author: "Ryan Herren"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

This is Ryan Herren's document for analysis on chocolate ratings.

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
hist(choco$Rating, main = "Histogram of Chocolate Ratings", xlab = "Rating")
```
  
  This histogram is skew left, with most ratings being between 2.5 and 4.

```{r}
boxplot(choco$Rating, main = "Boxplot of Chocolate Ratings", ylab = "Rating")
```
  
  There are a four outliers, which all come with ratings at or under 2.0

```{r}
barplot(table(choco$Location), las = 2, cex.names = 0.6)
```
  
  The USA has the most number of ratings by a lot. The three countries with the most ratings besides the USA are the UAE, France, and Brazil.
```{r}
cor(choco$Cocoa_Percent, choco$Rating)
summary(choco[c("Cocoa_Percent", "Rating")])
plot(choco$Rating, choco$Cocoa_Percent, xlab = "Rating", ylab = "Percentage of Cocoa")
```
  
  From this, we conclude that there isn't a correlating between the percentage of cocoa and the rating. Notably, there is only one chocolate that has a percentage of cocoa above 80% that received a 4.0 score.

